Comparison of Catalogs

### 2024-07-28 compare/compare.qmd
galaxy table + percent hist

@@

```{python}
def relative_diff(hec, lcv):
    diff = 100*(hec - lcv) / hec
    diff[np.isinf(diff)] = np.nan
    return diff
```

@@

## Scatter Grid
```{python}
vel_data = dt[["RVel", "V", "VLG", "cz", "V_VIR"]].to_pandas()

# Create a pair grid
sns.pairplot(vel_data, corner=True)
plt.show()
```
[?] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
## Heatmap
```{python}
# Compute the correlation matrix
corr_matrix = vel_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of Velocity Values")
plt.show()
```

:::

@@

@@

```
**Percentage change:**
```{python}
dt["diff_T"] = relative_diff(dt["T"], dt["TType"])
dt["diff_T"].info("stats")
```
```{python}
sns.distplot(dt["diff_T"])
plt.xlabel("Percentage change of Types of Galaxies")
plt.show()
```
As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0

## Inclanation
```{python}
scatter_plot(dt["inc"], dt["INCL"], sigma =True)
```

```{python}
dt["diff_inc"] = relative_diff(dt["INCL"], dt["inc"])
dt["diff_inc"].info("stats")
```
```{python}
sns.distplot(dt["diff_inc"])
plt.xlabel("Percentage change of the inclination of the galaxies [%]")
plt.show()
```

@@

```{python}
scatter_plot(dt["a26_1"], dt["R1"])
```
it is not very clear if we truly have a correlation or not. We need to see the linear correlation of the decimal logarithms.

```{python}
dt["log_a26"] = np.log(dt["a26_1"].data)
dt["log_a26"].unit = u.arcmin
dt["log_R1"] = np.log(dt["R1"].data)
dt["log_R1"].unit = u.arcmin
dt["log_R1"].info
```
```{python}
scatter_plot(dt["log_a26"], dt["log_R1"], sigma = True)
```

:::

## Luminosities

@@

::: panel-tabset
## B mag
```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
```

@@

scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
```
:::
## Absorpsion

@@

@@

@@

::: panel-tabset
## Heatmap
```{python}
#| echo: false
sfr_data.drop("logSFR_GSW", axis=1, inplace=True)
# Compute the correlation matrix
corr_matrix = sfr_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of SFR Values")
plt.show()
```
## Scatter Grid
```{python}
# Create a pair grid 
sns.pairplot(sfr_data, corner=True)
plt.show()

```
:::
It is possible we dont see a good correlation because we dont have a big enough common sample

>>>>

<!-- -->

@@

```{python}
def relative_diff(hec, lcv):
    diff = (hec - lcv) *100/ hec
    diff[np.isinf(diff)] = np.nan
    return diff
```

@@

## Scatter Grid

```{python}
vel_data = dt[["RVel", "V", "VLG", "cz", "V_VIR"]].to_pandas()

# Create a pair grid
sns.pairplot(vel_data, corner=True)
plt.show()
```

\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference. \## Heatmap

```{python}
# Compute the correlation matrix
corr_matrix = vel_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of Velocity Values")
plt.show()
```
:::

@@

```{=html}
<table style="border-collapse:collapse;border-spacing:0" class="tg"><thead>
<tr><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Hubble stage T </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−6 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−5 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−4 </th>
<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−3 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−2 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−1 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">0 </th>
<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">1 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">2 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">3 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">4 </th>
<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">5 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">6 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">7 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">8 </th>
<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">9 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">10 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">11 </th></tr>
</thead>
<tbody>
<tr><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">de Vaucouleurs class </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">cE </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">E </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">E+ </td>
<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0− </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S00 </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0+ </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0/a </td>
<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sab </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sbc </td>
<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sc </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Scd </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sd </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sdm </td>
<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sm </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Im </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"> </td></tr>
<tr><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Approximate Hubble class </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">E </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">S0 </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0/a </td>
<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa-b </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb-c </td>
<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">Sc </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sc-Irr </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Irr I </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"></td>
<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"></td></tr>
</tbody></table>

@@

**Percentage change:**

```{python}
dt["diff_T"] = relative_diff(dt["T"], dt["TType"])
dt["diff_T"].info("stats")
```

```{python}
sigma_T = sigma_clip(dt["diff_T"])
sigma_T.info("stats"), dt["diff_T"].info("stats")
```

```{python}
sns.histplot(dt["diff_T"], kde = True, label="Unclipped data")
sns.histplot(sigma_T, kde = True, label = "Sigma=3")
plt.title("Percentage change Distribution [%]")
plt.xlim([-200, 200])
plt.xlabel("Types of Galaxies")
plt.legend()
plt.show()
```

As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0

## Inclanation

```{python}
scatter_plot(dt["inc"], dt["INCL"], sigma =True)
```

```{python}
dt["diff_inc"] = relative_diff(dt["INCL"], dt["inc"])
dt["diff_inc"].info("stats") 
```

```{python}
sns.histplot(dt["diff_inc"], kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"Inclination of the galaxies [{dt['inc'].unit}]")
plt.show()
```

@@

```{python}
scatter_plot(dt["a26_1"], dt["R1"])
```

it is not very clear if we truly have a correlation or not. We need to see the linear correlation of the decimal logarithms.

```{python}
dt["log_a26"] = np.log10(dt["a26_1"].data)
dt["log_a26"].unit = u.arcmin
dt["log_R1"] = np.log10(dt["R1"].data)
dt["log_R1"].unit = u.arcmin
dt["log_R1"].info
```

```{python}
scatter_plot(dt["log_a26"], dt["log_R1"], sigma = True)
```

:::
## Luminosities

@@

::: panel-tabset
## B mag

```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
```

@@

scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
```

```{python}
dt["diff_K_mag"] = relative_diff(dt["Kmag"], dt["K"])
dt["diff_K_mag"].info("stats")
```

```{python}
sns.histplot(dt["diff_K_mag"], kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
plt.show()
```
:::

## Absorpsion

@@

::: panel-tabset
## Galactic

@@

## Internal

```{python}
plt.scatter(dt["AB_int"],dt["AI"],)
plt.xlabel(f"LCV, AB_int [{dt['AB_int'].unit}]")
plt.ylabel(f"HECATE, AI [{dt['AI'].unit}]")
plt.yscale("log")
plt.show()
```

If we use the decimal logarithm of the data we can clearly see the linear correlation.

```{python}
sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
```
:::

@@

```{python}
#| echo: false
sfr_data.drop("logSFR_GSW", axis=1, inplace=True)
# Compute the correlation matrix
corr_matrix = sfr_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of SFR Values")
plt.show()
```

## Scatter Grid

```{python}
# Create a pair grid 
sns.pairplot(sfr_data, corner=True)
plt.show()

```
:::

It is possible we dont see a good correlation because we dont have a big enough common sample
